SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-06-29 scipy-1.0/paper.tex
Early draft of language choices subsection.

\subsection*{Language preferences}

>>>>

\subsection*{Language choices}
Python / Cython, Fortran, C and C++ are the programming languages
used to implement scientific algorithms in the SciPy library. An analysis
of our code base using the \texttt{linguist} library provides a detailed
breakdown as \% composition by programming language in SciPy
(Figure~\ref{fig:linguist}).

    \begin{figure}[H]
        \centering
        \includegraphics[width=\textwidth]{static/linguist}
        \caption{The breakdown of programming languages used in the
	         SciPy library determined using the linguist library.
		 Small ($<0.5 \%$) amounts of TeX, Matlab, Shell,
		 and Makefile are excluded for clarity and mostly
		 provide supporting roles in tests, building, and
		 documentation.}
        \label{fig:linguist}
    \end{figure}
